\documentclass[letterpaper]{report}
\usepackage[utf8x]{inputenc} 
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage[margin=2cm]{geometry}
\usepackage{graphicx}
\usepackage[Sonny]{fncychap}
%\usepackage[]{fncychap}
\usepackage{enumitem}%avoid space in itemize
\usepackage{amsmath} %necessary to use \boxed{} in math mode
%\newcommand{\der}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}} %Derivata totale
%\usepackage{symate}
\begin{document}


\selectlanguage{english}
\chapter{Progression Review - year 2017-2018  \\ $\text{ } $ \\ Giorgio Manzoni}

\section{PAU Survey validation}
\begin{enumerate}
\item Comparing photometric and spectroscopic redshifts
\item Checking the completeness in the number of filters
\item Parent spectroscopic survey: CFHTLS and CFHTLenS. Analysis of the best definition of radius to be used for the forced photometry in the W3 field.
\item Analysis of any potential BIAS due to the Star-galaxy separation.
\item Building an empirical relation for the BPT diagram to help the Photo-z code retrieving more reliable redshifts.
\end{enumerate}

\section{PAU Survey observational run 18-25/03/2018}
\begin{enumerate}
\item Telescope settings: calibrating Bias/Dark/Flat Field
\item Observation of galaxies in W1 and W3 fields.
\end{enumerate} 

\section{Procter $\&$ Gamble - 2 month team project}
\begin{enumerate}
\item Optimization of the density of the laundry powder adapting the LASSO technique in an innovative way in order to fit the data minimising the number of parameters.
\end{enumerate}

\section{Workshop Emission Line Galaxies (Teruel - Spain)}
\begin{enumerate}
\item Presentation of my master project on the evolution of the colour-mgnitude relation using the VIPERS spectroscopic data.
\end{enumerate}

\section{GALFORM}
\begin{enumerate}
\item Trying to run GALFORM turning the AGN feedback on and off in order to get constraints on the quenching of star-formation in galaxies. The results might help in the publication of a paper related to my master project.
\end{enumerate}

\end{document}
 